---
title: "serosurvr-example"
author: "Rahul Arora"
output: html_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Set File Options

```{r fileopts}
# whether to import new data or use cached data
import_new_data = TRUE

# path to cache folder to read from and write to for this project
path_to_cache_folder = ".cache/example_analysis"

# set random seed
set.seed(12345)
```

## Load Necessary Libraries

SeroTracker research code also uses the `tidyverse`, an ecosystem of data analysis tools including libraries like `ggplot2`, `dplyr`, and `tibble`. Prioritize finding and implementing `tidyverse` approaches to your data input, transformation, and plotting needs, where possible.

```{r tidyverse}
library(tidyverse)
```

The custom `serosurvr` library is contained in a [public GitHub repo](https://github.com/serotracker/serosurvr): `serotracker/serosurvr`.

```{r serosurvr}
library("devtools")
devtools::install_github("serotracker/serosurvr")
library("serosurvr")      # load newest serosurvr
```
## Get Data

### Sample Data Request

Sample functions that demonstrate how to get data.

```{r getdata}

#create a data request
fs_males_req <- serosurvr::datareq_params(reqname = "france_spain_males",
                                          research_fields = TRUE,
                                          prioritize_estimates = TRUE,
                                          prioritize_estimates_mode = "analysis_dynamic",
                                          publication_end_date = "2020-12-31",
                                          filters = list())

# pipe data request to get_data function to request data
fs_males_tbl <-
  fs_males_req %>%
  serosurvr::get_data(import_new_data = import_new_data,
                      path_to_cache_folder = path_to_cache_folder)

fs_males_tbl

```

### Get Filter Options for Data Requests

Get a list of the filter options that can be used in data requests.

```{r filtopts}
serosurvr::filter_options()
```

## Clean Data

Sample functions that demonstrate how to clean data.

```{r cleandata}
# enforce_st_dtypes enforces correct dtypes on all columns
fs_males_tbl_cleaned <-
  fs_males_req %>%
  serosurvr::get_data(import_new_data = import_new_data,
                      path_to_cache_folder = path_to_cache_folder) %>%
  serosurvr::enforce_st_dtypes()

fs_males_tbl_cleaned
```
